### 2023-01-10 definitions.tex
Some small update
Up

\begin{lemma}  
If $\leq$ is a wqo then any infinite increasing sequence $I_0 \subseteq I_1 \subseteq I_2 \subseteq \cdots$ of
upward-closed sets eventually stabilizes, i.e. there is a $k \in N$ such that 
$I_k = I_{k+1} = I_{k+2} = \cdots $.
\end{lemma}

@@

\begin{definition}{ (index)}. 
For an upward-closed set $I \subseteq S$ and $k \geq 0$, let $I^k= \bigcup_{0 \leq j \leq k} pre^j(I)$.
The {\em index} $k(I)$ is the
smallest $k_0$ s.t. $I^k = I^{k_0}$ for all $k \geq k_0$.
\end{definition}

\begin{fact}\label{stop condition}
% Fact 4 (stop condition). 
Let $I \subseteq S$ be an upward-closed set and $k \geq 0$ s.t. $I^k = I^{k+1}$ , then $I^\ell = I^k$ for all $\ell \geq k$, i.e.,
$k(I) \leq k$. This also implies that $pre^* (I) = I^k $.
\end{fact}

>>>>

\begin{lemma}  \label{upward-closed stablizes}
If $\leq$ is a wqo then any infinite increasing sequence $I_0 \subseteq I_1 \subseteq I_2 \subseteq \cdots$ of
upward-closed sets eventually stabilizes, i.e. there is a $k \in N$ such that 
$I_k = I_{k+1} = I_{k+2} = \cdots $.
\end{lemma}

@@

\begin{definition}{ (index)}. 
If $S$ is a WSTS with strong monotony and $I \subseteq S$  is an upward-closed set and $k \geq 0$, let $I^k= \bigcup_{0 \leq j \leq k} pre^j(I)$.
The {\em index} $k(I)$ is the
smallest $k_0$ s.t. $I^k = I^{k_0}$ for all $k \geq k_0$.
\end{definition}

If $S$ is a WSTS with strong monotony and $I \subseteq S$ is an upward-closed set, the sets $\pred(I )$, and $\pred^{\geq k}(I )$ for
every $k \geq 0$ are upward-closed, thus Lemma~\ref{upward-closed stablizes} ensures the existence of $k(I)$.
Remark that $I^{k+1} = I \cup \pred(I^k)$, 
%thus $I^{k+1} = I^k$ implies $k(I) \leq k$.
which ensures the following.

\begin{fact}\label{stop condition}
% Fact 4 (stop condition). 
If $S$ is a WSTS with strong monotony and $I \subseteq S$ is an upward-closed set and $k \geq 0$ s.t. $I^k = I^{k+1}$ , then $I^\ell = I^k$ for all $\ell \geq k$, i.e.,
$k(I) \leq k$. This also implies that $\pred^*(I) = I^k$.
\end{fact}
